% !TeX root = RJwrapper.tex
\title{Variable Importance Plots: An Introduction to the \pkg{vip} Package}
\author{by Brandon M. Greenwell and Bradley C. Boehmke}

\maketitle

\abstract{
In the era of “big data”, it is becoming more of a challenge to not only build state-of-the-art predictive models, but also gain an understanding of what’s really going on in the data. For example, it is often of interest to know which, if any, of the predictors in a fitted model are relatively influential on the predicted outcome. Some modern algorithms—like random forests and gradient boosted decision trees—have a natural way of quantifying the importance or relative influence of each feature. Other algorithms—like naive Bayes classifiers and support vector machines—are not capable of doing so and model-agnostic approaches are generally used to measure each predictor’s importance. Enter \pkg{vip}, an R package for constructing variable importance scores/plots for many types of supervised learning algorithms using model-based and novel model-agnostic approaches.
}


% ------------------------------------------------------------------------------
\section{Introduction}
% ------------------------------------------------------------------------------

Variable importance (VI).


% ------------------------------------------------------------------------------
\section{Model-specific VI}
% ------------------------------------------------------------------------------

TBD.


% ------------------------------------------------------------------------------
\section{Model-agnostic VI}
% ------------------------------------------------------------------------------

TBD.


% ------------------------------------------------------------------------------
\section{A TensorFlow example}
% ------------------------------------------------------------------------------

TBD.


% ------------------------------------------------------------------------------
\section{Summary}
% ------------------------------------------------------------------------------

TBD.


\bibliography{pkg-vip}

\address{Brandon M. Greenwell\\
  Department of Mathematics and Statistics\\
  Wright State University\\
  3640 Colonel Glenn Hwy\\ 
  Dayton, OH 45435\\
  United States of America\\
  ORCiD: \href{https://orcid.org/0000-0002-8120-0084}{0000-0002-8120-0084}\\
  \email{greenwell.brandon@gmail.com}}

\address{Bradley C. Boehmke\\
  University of Cincinnati\\
  2925 Campus Green Dr\\
  Cincinnati, OH 45221\\
  United States of America\\
  ORCiD: \href{https://orcid.org/0000-0002-3611-8516}{0000-0002-3611-8516}\\
  \email{bradleyboehmke@gmail.com}}
